SIR Model With Testing Flows and Isolation

### 2021-01-22 codes/sir_macpan.Rnw
bib update

## fit beta0 based on the report data:
fitted.mod <- calibrate(
  data = df_covid_on
  , start_date = startdate
  ## skip breaks that are present by default:
  , time_args = list(break_dates = NULL)
  , base_params = params1obs
  , opt_pars = opt_pars
  , debug_plot = TRUE # instructive plotting during optimization
  , use_DE= FALSE
  , DE_lwr=c(6,-2,-2),
  , DE_upr=c(12,2,2)
)

>>>>

## fit beta0 based on the report data:
fitted.mod <- calibrate(
  data = df_covid_on
  , start_date = startdate
  ## skip breaks that are present by default:
  , time_args = list(break_dates = NULL)
  , base_params = params1obs
  , opt_pars = opt_pars
  , debug_plot = TRUE # instructive plotting during optimization
  , use_DE= FALSE ## use differential evolution algorithm
  , DE_lwr=c(6,-2,-2),
  , DE_upr=c(12,2,2)
)
